---
title: "Hands-On Programming with R"
author: "Zachary McKay"
date: "2022-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(readr)
library(tidyverse)
```

## R Interface

Create a number object, and then perform a series of arithmetic functions on it

```{r, include = FALSE}
num <- 6
num <- num + 2
num <- num * 3
num <- num - 6
num <- num / 3

number_circulator <- function(number) {
  ((((number + 2) * 3) - 6) / 3)
}
new_num <- 0

new_num <- number_circulator(num)

```

## Create a set of virtual dice and roll function

First, create a die object containing six numbers 1:6.

```{r, include = FALSE}
die <- 1:6

```

Next, create a function to roll the dice. Make sure to include replacement.

```{r, include = FALSE}
roll_pair <- function() {
  dice <- sample(x = die, size = 2, replace = TRUE)
  sum(dice)
}

roll_pair()


```

Next, create a function that accepts arguments so that we can roll different kinds of dice.

```{r, include = FALSE}
roll2_pair <- function(bones = 1:6) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
roll2_pair()

```

View how qplot works

```{r, echo = FALSE}
x <- c(-1, -.8, -.6, -.4, -.2, 0, .2, .4, .6, .8, 1)
y <- x^3
qplot(x, y)

```

Visualize using a historgram

```{r, echo = FALSE}
x <- c(1, 2, 2, 2, 3, 3)
qplot(x, binwidth = 1)

x2 <- c(1, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 4)
qplot(x2, binwidth = 1)

x3 <- c(0, 1, 1, 2, 2, 2, 3, 3, 4)
qplot(x3, binwidth = 1)
```

Roll the dice many times and visualize the distribution of results

```{r, echo = FALSE}
replicate(10, roll_pair())
replicate(1000, roll_pair())
rolls <- replicate(10000, roll_pair())
qplot(rolls, binwidth = 1)

```

Create weighted dice and visualize the results

```{r, echo = FALSE}
?sample
weight <- c(1/8, 1/8, 1/8, 1/8, 1/8, 3/8)

roll_weighted_pair <- function() {
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE, prob = weight)
  sum(dice)
}
rolls_weighted <- replicate(1000, roll_weighted_pair())
qplot(rolls_weighted, binwidth = 1)
```

## Playing Cards

First, create a deck of cards

```{r, echo = FALSE}
hand <- c("ace", "king", "queen", "jack", "ten")
typeof(hand)
attributes(hand)
names(die) <- c("one", "two", "three", "four", "five", "six")
attributes(die)
royal_cards <- c("ace", "king", "queen", "jack", "ten")
spades <- replicate(5, "spades")
royal_flush <- c(royal_cards, spades)
royal_flush <- matrix(royal_flush)
dim(royal_flush) <- c(5,2)
card_type <- factor(c("face", "number", "ace"))
card <- list("ace", "hearts", 1)
typeof(card)
deck <- data.frame(face = c("ace", "two", "six"),
                   suit = c("clubs", "clubs", "clubs"),
                   value = c(1, 2, 3))
face = c("two", "three", "four", "five", "six", "seven",
         "eight", "nine", "ten", "jack", "queen", "king",
         "ace")

face_deck = replicate(4, face)
suit_deck = c(replicate(13, "clubs"), replicate(13,"hearts"),
              replicate(13, "spades"), replicate(13,
                                                 "diamonds"))
value_deck = replicate(4, c(2:13, 11))
dim(value_deck) <- c(52, 1)

deck <- data.frame(face = face_deck, suit = suit_deck,
                   value = value_deck)

str(deck)
deck

```

Alternatively, import deck from a .csv file and save it as a new .csv file.

```{r}
deck <- read_csv("deck.csv")
View(deck)
head(deck)
tail(deck)
write.csv(deck, file = "cards.csv", row.names = FALSE)
cards <- read_csv("cards.csv")
head(cards)
tail(cards)
```

Write deal function to deal a card and shuffle the deck

```{r}
hand <- NULL
deal_to_hand <- function(hand, cards) {
  if(hand %>% is.null()) {
   hand <- data.frame(cards[1, ])
  } else {
    hand <- hand %>%
            add_row(cards[1,])
  }
}
deal_from_deck <- function(cards) {
  cards[-1,]
}

shuffle <- function(deck) {
  random <- sample(1:52, size = 52, replace = FALSE)
  deck[random, ]
}
hand <- NULL

shuffled_deck <- shuffle(deck)
head(shuffled_deck)
sum(shuffled_deck$value)
sum(deck$value)
hand <- deal_to_hand(hand, shuffled_deck)
shuffled_deck <- deal_from_deck(shuffled_deck)
hand <- deal_to_hand(hand, shuffled_deck)
hand1 <- NULL
hand2 <- NULL
for (i in 1:5) {
  hand1 <- deal_to_hand(hand1, shuffled_deck)
  shuffled_deck <- deal_from_deck(shuffled_deck)
  hand2 <- deal_to_hand(hand2, shuffled_deck)
  shuffled_deck <- deal_from_deck(shuffled_deck)
}
shuffle_war_deck <- function(deck) {
  for(i in 1:length(deck)) {
    if(deck[i, "face"] == "ace") {
      deck[i, "value"] = 14
    }
  }
  random <- sample(1:52, size = 52, replace = FALSE)
  deck[random, ]
}
war_deck <- shuffle_war_deck(deck)


```

