---
title: "Hands-On Programming with R"
author: "Zachary McKay"
date: "2022-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## R Interface

Create a number object, and then perform a series of arithmetic functions on it

```{r, include = FALSE}
num <- 6
num <- num + 2
num <- num * 3
num <- num - 6
num <- num / 3

number_circulator <- function(number) {
  ((((number + 2) * 3) - 6) / 3)
}
new_num <- 0

new_num <- number_circulator(num)

```

## Create a set of virtual dice and roll function

First, create a die object containing six numbers 1:6.

```{r, include = FALSE}
die <- 1:6

```

Next, create a function to roll the dice. Make sure to include replacement.

```{r, include = FALSE}
roll_pair <- function() {
  dice <- sample(x = die, size = 2, replace = TRUE)
  sum(dice)
}

roll_pair()


```

Next, create a function that accepts arguments so that we can roll different kinds of dice.

```{r, include = FALSE}
roll2_pair <- function(bones = 1:6) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
roll2_pair()

```

View how qplot works

```{r, echo = FALSE}
x <- c(-1, -.8, -.6, -.4, -.2, 0, .2, .4, .6, .8, 1)
y <- x^3
qplot(x, y)

```

Visualize using a historgram

```{r, echo = FALSE}
x <- c(1, 2, 2, 2, 3, 3)
qplot(x, binwidth = 1)

x2 <- c(1, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 4)
qplot(x2, binwidth = 1)

x3 <- c(0, 1, 1, 2, 2, 2, 3, 3, 4)
qplot(x3, binwidth = 1)
```

Roll the dice many times and visualize the distribution of results

```{r, echo = FALSE}
replicate(10, roll_pair())
replicate(1000, roll_pair())
rolls <- replicate(10000, roll_pair())
qplot(rolls, binwidth = 1)

```

Create weighted dice and visualize the results

```{r, echo = FALSE}
?sample
weight <- c(1/8, 1/8, 1/8, 1/8, 1/8, 3/8)

roll_weighted_pair <- function() {
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE, prob = weight)
  sum(dice)
}
rolls_weighted <- replicate(1000, roll_weighted_pair())
qplot(rolls_weighted, binwidth = 1)
```

## Playing Cards
